\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS7 Cook}
\author{natcook97 }
\date{March 2021}

\begin{document}

\maketitle
\begin{table}
\centering
\begin{tabular}[t]{lrrrrrrr}
\toprule
  & Unique (\#) & Missing (\%) & Mean & SD & Min & Median & Max\\
\midrule
logwage & 670 & 25 & 1.6 & 0.4 & 0.0 & 1.7 & 2.3\\
hgc & 16 & 0 & 13.1 & 2.5 & 0.0 & 12.0 & 18.0\\
tenure & 259 & 0 & 6.0 & 5.5 & 0.0 & 3.8 & 25.9\\
age & 13 & 0 & 39.2 & 3.1 & 34.0 & 39.0 & 46.0\\
\bottomrule
\end{tabular}
\end{table}

\begin{enumerate}
    \item 25 percent of logwage values are missing. I would guess that the observations are most likely MNAR. 
    \item Each of the estimates from the models are less than the true value of 0.093. Model 1 with the list-wise deletion gives the largest and closest estimate followed by model 3 which used the predicted value from the complete cases regression. I can't get Model 4 to run but it is probably the most legit method. Model 1 is not ideal because the observations are almost certainly not MCAR. Model 2 will cause the variance to drop which we see in the relatively lower F stat. Models 3 and 4 are probably the best for imputing the missing values. 
    \item Progress on the project is not so bueno. I haven't landed on a data set yet but I'd like to find one/a topic that's fairly straightforward and just gives me a good opportunity to apply the techniques we've been learning. I don't feel like I need to cure cancer necessarily with this research - meaning if I just confirm returns to education or something like that I will be happy. 
\begin{table}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & 0.534 & 0.708 & 0.563\\
 & (0.146) & (0.116) & (0.112)\\
hgc & 0.062 & 0.050 & 0.059\\
 & (0.005) & (0.004) & \vphantom{1} (0.004)\\
as.factor(college)not college grad & 0.145 & 0.168 & 0.177\\
 & (0.034) & (0.026) & (0.025)\\
poly(tenure, 2, raw = T)1 & 0.050 & 0.038 & 0.047\\
 & (0.005) & (0.004) & (0.004)\\
poly(tenure, 2, raw = T)2 & -0.002 & -0.001 & -0.002\\
 & (0.000) & (0.000) & (0.000)\\
age & 0.000 & 0.000 & 0.000\\
 & (0.003) & (0.002) & (0.002)\\
as.factor(married)single & -0.022 & -0.027 & -0.028\\
 & (0.018) & (0.014) & (0.013)\\
\midrule
Num.Obs. & 1669 & 2229 & 2229\\
R2 & 0.208 & 0.147 & 0.223\\
R2 Adj. & 0.206 & 0.145 & 0.221\\
AIC & 1179.9 & 1091.2 & 956.8\\
BIC & 1223.2 & 1136.8 & 1002.4\\
Log.Lik. & -581.936 & -537.580 & -470.382\\
F & 72.917 & 63.973 & 106.573\\
\bottomrule
\end{tabular}
\end{table}


\end{enumerate}
\end{document}
